### 2023-01-27 definitions.tex
details

A \emph{downward-WSTS} is ... \\

@@

\begin{corollary}
{\sc resilience} is decidable for WSTS with strong upward compatibility and such that $\uparrow post^*(S)$ is computable.
\end{corollary}

>>>>

@@

\begin{corollary}\label{postcomputable}
{\sc resilience} is decidable for WSTS with strong upward compatibility and such that $\uparrow post^*(S)$ is computable.
\end{corollary}

### 2023-01-27 proof.tex
Harmonizing notations Pred Pre & pre
Searching for counter-examples
details

\section{Decidability for WSTS with downward/strong upward compatibility}

\begin{lemma}
Let $A \subseteq S$, $J \subseteq S$ downward-closed and $I \subseteq S$ upward-closed. 
Then $A \cap J \subseteq I$  iff $ (\uparrow  A) \cap J \subseteq I$.
\end{lemma}

@@

This result is not in xxx and don't use the problematic hypothsis on $post^*$.

@@

We define inductively
$I^{k} = \bigcup_{0 \leq j \leq k} pre^j(I)$. Note that for all $k \in \N$, $I^k$ is upward-closed due to
the strongly upward compatibility of $(S, \rightarrow, \leq)$.

@@

\begin{theorem}
{\sc bounded resilience} and {\sc resilience} is decidable for WSTS with downward/strong upward compatibility.
\end{theorem}

>>>>

\section{Decidability of resilience for downward-WSTS}

Let us recall the definition of downward-WSTS.

\begin{definition} \cite{DBLP:journals/tcs/FinkelS01}
A \emph{downward-WSTS} is an ordered transition system $(S, \rightarrow, \leq)$
such that $\leq$ is a wqo and
%  decidable ≤  wqo on S, i.e., for each two given states s, s ′ ∈ S, it is decidable whether s ≤ s ′ . 
the transition relation $ \rightarrow$ is downward-compatible with $\leq$, i.e., for all  transition $s_1 \rightarrow t_1$
with $s_1, t_1 , s_2 \in S$
	and $s_2 \leq s_1$, there exists a transition $s_2 \rightarrow^{*} t_2$ with $t_2 \leq t_1$. 		
\end{definition}

%		enlever l'hypothèse finitely branching ?
A downward-WSTS has the \emph{reflexive} compatibility if for all transition  $s_1 \rightarrow t_1$ with
$s_1, t_1 , s_2 \in S$ and $s_2 \leq s_1$, either $t_1 \leq s_2$ or there exists a transition $s_2 \rightarrow t_2$ with $t_2 \leq t_1$.

Downward-WSTS enjoy a nice reachability property.

\begin{theorem}[Proposition 5.4 in \cite{DBLP:journals/tcs/FinkelS01}]
%	Since by Proposition 5.4 in \cite{DBLP:journals/tcs/FinkelS01}, we know that  
For finitely branching downward-WSTS $(S, \rightarrow, \leq)$, with reflexive compatibility, decidable $\leq$ and effective $post$, a finite basis of $\uparrow post^*(s_0)$ is computable for any $s_0 \in S$.
\end{theorem}

%	Let us say that a downward-WSTS is \emph{effective}
Using Corollary \ref{postcomputable}, we deduce that resilience is decidable for finitely branching downward-WSTS with reflexive compatibility and with strong upward compatibility, with a decidable $\leq$ and an effective $post$.

%%%%%
\alain{peut-on faire mieux ?}

\begin{lemma}\label{Lemma intersection}
Let $A \subseteq S$, $J \subseteq S$ downward-closed and $I \subseteq S$ upward-closed. 
Then $A \cap J \subseteq I$  iff $ (\uparrow  A) \cap J \subseteq I$.
\end{lemma}

@@

This result is not in xxx and don't use the problematic hypothsis on $post^*$.
\alain{ben si car downward-WSTS + qqhypothèses (voir plus haut) ont un $ \uparrow post^*(s)$ calculable !
peut-on faire sauter qq hypothèses ?  finitely branching ??? with reflexive compatibility ????}

@@

We define inductively
$I^{k} = \bigcup_{0 \leq j \leq k} \pred^j(I)$. Note that for all $k \in \N$, $I^k$ is upward-closed due to
the strongly upward compatibility of $(S, \rightarrow, \leq)$.

@@

\begin{theorem}
{\sc bounded resilience} and {\sc resilience} are decidable for WSTS with downward/strong upward compatibility.
\end{theorem}
